Check Coverage

### 2019-08-14 analysis/merge_data.Rmd
Switch to group_map, write out fd data for each site/plot

get_fd <- function(data){
  print(max(data$record_id))
  species_mat <- data %>%
    select(year, id) %>% 
    distinct() %>%
    arrange(year, id) %>%
    mutate(present = 1) %>%
    spread(id, value = present, fill = 0) %>%
    select(-year)

@@

  as.tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .)
}

@@

test_data <- biotime_traits %>% 
  group_by(study_id, plot) %>%
  nest() %>%
  mutate(metrics = map(data, ~get_fd_safe(.x))) %>%
  select(-data) %>%
  unnest()
```

>>>>

get_fd <- function(data, study, plot){
  print(max(data$record_id))
  species_mat <- data %>%
    select(year, id) %>% 
    distinct() %>%
    arrange(year, id) %>%
    mutate(present = 1) %>%
    spread(id, value = present, fill = 0) %>%
    select(-year)

@@

  dir.create(paste0(here::here("data"), "/fd_output"), showWarnings = FALSE)

  as.tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = study, plot = plot) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot, "_fd.tsv"))
}

@@

fd_data <- biotime_traits %>% 
  filter(study_id == 56) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd(.x, study = .y$study_id, plot = .y$plot))
```
